Submission and Formatting Instructions for the Twenty-Eighth \\ International Conference on Machine Learning (ICML 2012)

### 2012-04-10 klein2012/main.tex
Correction d'une typo signalée dans les revues :
l. 420: The authors probably want to say "complete expert policy".
Correction d'une typo mentionnée dans les revues :
There are some broken/misdirect links in lines 365, 532.

First, notice that each component $\mu_j^E$ of the expert feature
expectation $\mu^E$ is actually the $Q$-function of the expert
policy according to the reward function $\psi_j$, the $j^\text{th}$
basis function of the considered hypothesis space:
\begin{equation}
\mu^E_j(s,a) = E^{\pi_E}_{sa}[\sum\limits_{t=0}^\infty \gamma^t
\psi_j(s)].\label{eq:muE_bellman}
\end{equation}
Therefore, it satisfies the Bellman evaluation
equation~\eqref{Qdef.eqn}. Assuming that the expert policy and the
transition probabilities are known, the expert feature expectation
can be exactly computed.

@@

\begin{prop}
Under assumptions \ref{assumption1} and \ref{assumption2}, the
subgradient algorithm defined by the sequence $\theta_0=0$,
$\theta_{t+1}=\theta_t-\alpha_t\frac{g_{\theta_t}}{\|g_{\theta_t}\|_2}$
where $g_{\theta_t}=\sum_{s\in
S}\nu_E(s)(\mu^E_{sa^*}-\mu^E_{s\pi_E(s)})$ with
$a^*\in\argmax_{a\in A}\theta_t^T\mu^E_{sa}+l(s,a)$,
$\sum_{t\geq0}\alpha_t>\infty$ and $\sum_{t\geq0}\alpha_t^2<\infty$,
is convergent:
$\lim_{t\rightarrow+\infty}\theta_t=\tilde{\theta}\in\mathbb{R}^p$.
Moreover we have that
$J(\tilde{\theta})=\inf_{\theta\in\mathbb{R}^p}J(\theta)=0$. Finally
the expert policy $\pi_E$ is the unique optimal policy for the
reward $\tilde{\theta}^T\psi$.
\end{prop}
\begin{proof}
The cost function  $J$ is convex, proper, closed and with finite
values (the action space being finite). Therefore, using the result
of~\cite[section~5]{correa1993convergence} allows to conclude that
$\lim_{t\rightarrow+\infty}\theta_t=\tilde{\theta}\in\mathbb{R}^p$
and $J(\tilde{\theta})=\inf_{\theta\in\mathbb{R}^p}J(\theta)$.
%
Moreover, Lemma~\ref{proposition1} shows that
$\inf_{\theta\in\mathbb{R}^p}J(\theta)=0$.
%
So we have
$J(\tilde{\theta})=\inf_{\theta\in\mathbb{R}^p}J(\theta)=0$ which
means that $\tilde{\theta}\in M^*$ and satisfies equation
\eqref{existence.eq}. This implies that, $\forall s\in S$, $\forall
a\in A$:
\begin{equation}
\tilde{\theta}^T\mu^E_{s\pi_E(s)}>\tilde{\theta}^T\mu^E_{sa},
\end{equation}
which proves that the expert policy $\pi_E$ is the unique optimal
policy for the reward $\tilde{\theta}^T\psi$.
\end{proof}

>>>>

First, notice that each component $\mu_j^E$ of the expert feature
expectation $\mu^E$ is actually the $Q$-function of the expert
policy according to the reward function $\psi_j$, the $j^\text{th}$
basis function of the considered hypothesis space:
\begin{equation}
\mu^E_j(s,a) = E^{\pi_E}_{sa}[\sum\limits_{t=0}^\infty \gamma^t
\psi_j(s)].\label{eq:muE_bellman}
\end{equation}
Therefore, it satisfies the Bellman evaluation
equation~\eqref{Qdef.eqn}. Assuming that the complete expert policy and the
transition probabilities are known, the expert feature expectation
can be exactly computed.

@@

\begin{prop}
Under assumptions \ref{assumption1} and \ref{assumption2}, the
subgradient algorithm defined by the sequence $\theta_0=0$,
$\theta_{t+1}=\theta_t-\alpha_t\frac{g_{\theta_t}}{\|g_{\theta_t}\|_2}$
where $g_{\theta_t}=\sum_{s\in
S}\nu_E(s)(\mu^E_{sa^*}-\mu^E_{s\pi_E(s)})$ with
$a^*\in\argmax_{a\in A}\theta_t^T\mu^E_{sa}+l(s,a)$,
$\sum_{t\geq0}\alpha_t>\infty$ and $\sum_{t\geq0}\alpha_t^2<\infty$,
is convergent:
$\lim_{t\rightarrow+\infty}\theta_t=\tilde{\theta}\in\mathbb{R}^p$.
Moreover we have that
$J(\tilde{\theta})=\inf_{\theta\in\mathbb{R}^p}J(\theta)=0$. Finally
the expert policy $\pi_E$ is the unique optimal policy for the
reward $\tilde{\theta}^T\psi$.
\end{prop}
\begin{proof}
The cost function  $J$ is convex, proper, closed and with finite
values (the action space being finite). Therefore, using the result in section 5 
of~\cite{correa1993convergence} allows to conclude that
$\lim_{t\rightarrow+\infty}\theta_t=\tilde{\theta}\in\mathbb{R}^p$
and $J(\tilde{\theta})=\inf_{\theta\in\mathbb{R}^p}J(\theta)$.
%
Moreover, Lemma~\ref{proposition1} shows that
$\inf_{\theta\in\mathbb{R}^p}J(\theta)=0$.
%
So we have
$J(\tilde{\theta})=\inf_{\theta\in\mathbb{R}^p}J(\theta)=0$ which
means that $\tilde{\theta}\in M^*$ and satisfies equation
\eqref{existence.eq}. This implies that, $\forall s\in S$, $\forall
a\in A$:
\begin{equation}
\tilde{\theta}^T\mu^E_{s\pi_E(s)}>\tilde{\theta}^T\mu^E_{sa},
\end{equation}
which proves that the expert policy $\pi_E$ is the unique optimal
policy for the reward $\tilde{\theta}^T\psi$.
\end{proof}
